Issues with Dynamical Measurements Across the Disk

### 2019-02-17 paper/ms.tex
Add citation to Bland-Hawthorn
Add more references to dynamical R0 measurements

These discoveries are all indicative that the Milky Way departs from
axisymmetry and is undergoing phase mixing and dynamical interactions across a
range of spatial and temporal scales. Underlying the quantitative description
of the mechanisms at work that give rise to these signatures is the assumption
of a Galactocentric coordinate system \citep{2008gady.book.....B} which can
both precisely and accurately be defined and measured. In angular coordinates,
the center of the galaxy is taken to be the location of
Sgr~A\textsuperscript{*} \citep[e.g.][]{2004ApJ...616..872R}. From stellar
motions near Sgr~A\textsuperscript{*}, the distance to the center is taken to
be $\sim 8.1\text{--}8.3\,\kpc$
\citep{2009ApJ...692.1075G,2018AA...615L..15G}. The vertical height is found
by identifying where the stellar positions and velocities reach a maximum
(effectively the median height of all disk stars), and is usually taken to be
$\sim 25\,\pc$ \citep{2001ApJ...553..184C}, with more recent measurements from
{\em Gaia} DR2 placing it at $\sim 20\,\pc$ \citep{2019MNRAS.482.1417B}.

@@

While we focus our discussion now solely on the midplane, there is an
additional complication in the measurement of the distance from the Sun to the
Galactic center that may also be important. When modelling stars at Galactic
radii close to the Sun's radius, it is in principle possible to determine what
point they are orbitting about, or in other words the ``dynamic Galactic
center.'' It is not guaranteed that this dynamic Galactic center will coincide
with the distance to Sgr~A\textsuperscript{*} \citep{2018AA...615L..15G}. In
fact, \citet{2015ApJ...803...80K} were able to measure the distance of the Sun
to the Galactic center using dynamical information on Palomar 5, though not to
a precision capable of competing with the distance to
Sgr~A\textsuperscript{*}.

>>>>

These discoveries are all indicative that the Milky Way departs from
axisymmetry and is undergoing phase mixing and dynamical interactions across a
range of spatial and temporal scales. Underlying the quantitative description
of the mechanisms at work that give rise to these signatures is the assumption
of a Galactocentric coordinate system \citep{2008gady.book.....B} which can
both precisely and accurately be defined and measured. In angular coordinates,
the center of the galaxy is taken to be the location of
Sgr~A\textsuperscript{*} \citep[e.g.][]{2004ApJ...616..872R}. From stellar
motions near Sgr~A\textsuperscript{*}, the distance to the center is taken to
be $\sim 8.1\text{--}8.3\,\kpc$
\citep{2009ApJ...692.1075G,2018AA...615L..15G}. The vertical height is found
by identifying where the stellar positions and velocities reach a maximum
(effectively the median height of all disk stars), and is usually taken to be
$\sim 25\,\pc$ \citep{2001ApJ...553..184C}, with more recent measurements from
{\em Gaia} DR2 placing it at $\sim 20\,\pc$ \citep{2019MNRAS.482.1417B}. A
pre-{\em Gaia} review of these measurements is given by
\citet{2016ARAA..54..529B}.

@@

While we focus our discussion now solely on the midplane, there is an
additional complication in the measurement of the distance from the Sun to the
Galactic center that may also be important. When modelling stars at Galactic
radii close to the Sun's radius, it is in principle possible to determine what
point they are orbitting about, or in other words the ``dynamic Galactic
center.'' It is not guaranteed that this dynamic Galactic center will coincide
with the distance to Sgr~A\textsuperscript{*} \citep{2018AA...615L..15G}. In
fact, \citet{2015ApJ...803...80K} were able to measure the distance of the Sun
to the Galactic center using the dynamical information of Palomar 5. Other
dynamical measurements of the Solar distance have been made, though none with
a precision capable of competing with the distance to Sgr~A\textsuperscript{*}
\citep{1981gask.book.....M,2011PASJ...63..867S,2012MNRAS.427..274S,2013AstL...39...95B,2013IAUS..289..444Z}.
